---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dpdr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/mattwarkentin/dpdr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mattwarkentin/dpdr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `dpdr` is to provide a programmatic interface to the Health Canada Drug Product Database API.

## Installation

You can install the development version of `dpdr` from [GitHub](https://github.com/mattwarkentin/dpdr) with:

``` r
# install.packages("remotes")
remotes::install_github("mattwarkentin/dpdr")
```

## Usage

There are 11 API endpoints as part of Health Canada's Drug Product Database API. Each of these endpoints will be demonstrated in the following sections.

```{r}
library(dpdr)
```

### Active Ingredient

We can search for active ingredient information based on the drug code...

```{r}
dpd_active_ingredient(id = 48905)
```

Or based on the name of a drug.

```{r}
dpd_active_ingredient(name = "afatinib")
```

### Company

We can search for information about a drug company:

```{r}
dpd_company(10825)
```

### Drug Product

The family of drug product functions allow us to query information about drug products based on the drug product code or drug identification number (DIN).

```{r}
dpd_drug_product(id = 2049)
```

```{r}
dpd_drug_product(din = '00326925')
```

We can also find the list of drugs based on the drugs product status.

```{r}
dpd_drug_product(status = 1)
```

Or, we can find the list of drugs based on the brand names.

```{r}
dpd_drug_product(brandname = "cidyl")
```

### Dosage Form

The dosage form is form of presentation in which the product is supplied. We can query dosage form based on the drug product code.

```{r}
dpd_dosage_form(10846)
```

### Packaging

We can query the information about package sizes based on the drug product code.

```{r}
dpd_packaging(11685)
```

### Pharmaceutical Standard

We can query the standard to which the drug product is manufactured and represented, based on the drug product code.

```{r}
dpd_pharm_standard(11534)
```

### Route of Administration

We can query the route of administration for a drug based on the drug product code.

```{r}
dpd_route_of_admin(3)
```

### Schedule

Each drug is assigned one or more schedules, we can query this based on the drug product code (see `?dpd_schedule` for more information).

```{r}
dpd_schedule(10687)
```

### Product Status

We can query the product status of a drug product.

```{r}
dpd_product_status()
```

### Therapeutic Class

We can query the Therapeutic Class according to a drugs main therapeutic use.

```{r}
dpd_therapeutic_class(10564)
```

### Veterinary Species

Lastly, we can query the species for a drug product based on the veterinary drug product code.

```{r}
dpd_vet_species(13755)
```

## Code of Conduct

Please note that the dpdr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
